Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-28 paper/virtual_cytoplasm_v2.tex
figure 1
Introduction

Crowding ... ~\cite{feig2017crowding} ~\citep{ostrowska2019modeling}

-> Crowding affects hydration around proteins ~\cite{Harada2012a,king2013crowding}
-> leads to stabilization of native structure due to the excluded volume effect ~\cite{cheung2005molecular}
-> can also destabilize proteins due to  ~\cite{feig2011variable,miklos2011protein,wang2012macromolecular}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{shrinking_volume.pdf} 
\includegraphics[scale=0.5]{box.pdf} 
% \includegraphics[scale=0.11]{box_big.png}
% \includegraphics[scale=0.11]{box_small_.png}
%\includegraphics[scale=0.5]{shrinking_density.pdf}

>>>>

The intracellular microenvironment is markedly different from the\textit{in vitro} simplification from which most of our current knowledge about the biochemical and biophysical behavior of macromolecules was derived~\cite{feig2017crowding}. Instead of simple and diluted, the \textit{in vivo} microenvironment is highly heterogeneous and concentrated, leading to spatial constrains that directly affects biological activities~\citep{ostrowska2019modeling}. Macromolecular crowding directly influences the stability of macromolecules. There is an equilibrium between stabilization of their native structure due to the entropic component given by the excluded volume effect~\cite{cheung2005molecular} and destabilizationg due to enthalpic component given by unspecific interactions with the crowders~\cite{feig2011variable,miklos2011protein,wang2012macromolecular}. Additionally, crowding affects the structure and dynamics of water around proteins, which has an indirect but important effect in their biological activities~\cite{Harada2012a,king2013crowding}.

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{box.pdf} 
\includegraphics[scale=0.5]{shrinking_volume.pdf} 
% \includegraphics[scale=0.11]{box_big.png}
% \includegraphics[scale=0.11]{box_small_.png}
%\includegraphics[scale=0.5]{shrinking_density.pdf}
